The `geomnet` package

### 2016-12-06 README.Rmd
fix HP plot to ignore singletons

```{r HPplot, fig.width=10, fig.align='center'}
library(geomnet)
head(hp.edges)
head(hp.chars)
hp.all <- fortify(as.edgedf(hp.edges), hp.chars, group = "book")
ggplot(data=hp.all, aes(from_id = from, to_id = to_id)) + 
  geom_net(fiteach=T, directed = T, size = 2, linewidth = .5, 
           ealpha = .5, labelon = T, fontsize = 2, repel = T, 
           labelcolour = "black", arrowsize = .5,
           aes(colour = house, group = house, shape = gender)) + 
  scale_colour_manual(values = c("#941B08","#F1F31C", 
                                 "#071A80", "#154C07")) + 
  facet_wrap(~book, labeller = "label_both") + 
  theme_net() + theme(panel.background = element_rect(colour = 'black'))
```

>>>>

```{r HPplot, fig.width=10, fig.height=8, fig.align='center'}
library(geomnet)
head(hp.edges)
head(hp.chars)
hp.all <- fortify(as.edgedf(hp.edges), hp.chars, group = "book")
# only plot the characters with any connections in a given book. 
hp.sub <- NULL
for (i in 1:6){
  dat <- filter(hp.all, book == i)
  singletons <- dat$from[is.na(dat$to_id)]
  true_singletons <- singletons[!singletons %in% unique(dat$to_id)[-1]]
  dat2 <- dat[!dat$from %in% true_singletons,]
  hp.sub <- rbind(hp.sub, dat2)
}
ggplot(data=hp.sub, aes(from_id = from, to_id = to_id)) + 
  geom_net(fiteach=T, directed = T, size = 2, linewidth = .5, 
           ealpha = .5, labelon = T, fontsize = 2, repel = T, 
           labelcolour = "black", arrowsize = .5,
           aes(colour = house, group = house, shape = gender)) + 
  scale_colour_manual(values = c("#941B08","#F1F31C", 
                                 "#071A80", "#154C07")) + 
  facet_wrap(~book, labeller = "label_both") + 
  theme_net() + theme(panel.background = element_rect(colour = 'black'))
```
